### 2016-08-30 rebuttal.tex

\begin{questions}

\question Explaining what Python is (lines 70--72) should go before talking about SymPy as a ``CAS written in Python''. Further, the paper assumes a moderate familiarity with Python (for example, Python's console, OOP, and exceptions), and this should be specified. There should be a short note on the used Python console (\texttt{>>>} is the prompt, with the results of computation following immediately in the lines after it). The citation [25] from line 65 should be moved next to ``Python'' in line 70.
\begin{solution}
  The citation was moved and a footnote for the Python interactive prompt was
  added where it was used first time. We have also added a footnote indicating
  a moderate familiarity with Python is assumed.
\end{solution}

\question Line 73 has outdated information. Sage was renamed to SageMath and it no longer aims only at pure mathematics but also at algebra, numerical analysis, etc. The reference [40] should be replaced by a more up-to-date one.
\begin{solution}
We have updated the name and citation, and changed ``pure mathematics'' to
``pure and applied mathematics''.
\end{solution}

\question The plural ``CASs'' is usually written as ``CASes'' or ``CAS's'', with the latter being somewhat problematic due to it looking like it implies possession.
\begin{solution}
  Different style guides appear to disagree on the proper way to pluralize
  non-plural acronyms that end in ``S''. We have been informed by the PeerJ
  publishing staff that either form (``CASs'' or ``CAS's'') is acceptable, so
  long as we are consistent. We have chosen ``CAS's'' as suggested, and have
  changed all instances in the manuscript.
\end{solution}

### 2016-09-11 rebuttal.tex

\section{Reviewer 1}
\subsection{Basic reporting}
\begin{questions}
\question Generally good. A part that confused me is the assertion (footnote 3) that ``If
A and B are Symbols created with commutative=False then SymPy will keep A·B
and B·A distinct.'' Does that mean that BOTH of them must be created this way,
and that A and x (if x is created normally) will commute? Is there any way to
declare commutators? How does one guarantee that other pieces of code, e.g.
Gaussian elimination, respect non-commutativity?
\begin{solution}
  We have clarified the footnote. Both expressions must be set as
  \texttt{commutative=False}. Internally, in \texttt{Mul}, the ``commutative
  part'' of an expression is pulled out to the front and canonically ordered,
  and the ``noncommutative part'' is not reordered.

Commutators are implemented in the \texttt{sympy.physics.quantum} module and
are discussed in section 5.2.

Different algorithms do generally require special consideration for
noncommutative expressions to be correct. If an algorithm implicitly assumes
that expressions commute, it may return incorrect results when given a
noncommutative expression.
\end{solution}

\question References reasonable, though [8], an excellent reference, makes almost
precisely the opposite point to that for which it is cited --- ``simplification
is not well-defined''. I think the authors are trying to follow [8]'s
definition of simplification.
\begin{solution}
We agree that this is a bad reference, because we are not actually
using their definition.  Yes, that article rigorously define
``simplification'', but it's just one approach.  This citation
was replaced with a better reference, that illustrate our point.
\end{solution}
\end{questions}

@@

Kluyver, T., Ragan-Kelley, B., P{\'e}rez, F.,
Granger, B., Bussonnier, M., Frederic, J., Kelley, K., Hamrick, J., Grout,
J., Corlay, S., et al. (2016). Jupyter notebooks---a publishing format for
reproducible computational workflows. In \textit{Positioning and Power in Academic
Publishing: Players, Agents and Agendas: Proceedings of the 20th International
Conference on Electronic Publishing}, page 87. IOS Press.

as recommended by the Jupyter developers at \url{https://github.com/jupyter/jupyter/issues/190}.
\end{solution}

\question The word ``software'' in line 91 is ambiguous; ``library'' or ``package'' would make a better choice.
\begin{solution}
We have changed ``software'' to ``library''.
\end{solution}

\question Lines 91--96: ``we discuss/look at/etc'' is the preferred form, instead of ``section discusses/looks at/etc''.
\begin{solution}
We had decided not to use first person.  We prefer to be
consistent here, unless this does violate some journal policy,
which is not the case (see, for example,
\url{https://peerj.com/articles/cs-80/}).
\end{solution}

### 2016-09-11 rebuttal.tex

\question In line 495, the word ``solving'' seems more appropriate than ``solutions''.
\begin{solution}
This was replaced with ``solving ODEs''.
\end{solution}

\question In line 504 ``is'' should be used instead of ``are'' (because ``array'' is singular).
\begin{solution}
This was fixed.
\end{solution}

\question In line 518, ``produces'' should become plural.
\begin{solution}
This was fixed.
\end{solution}

\question The title of section 5, ``Domain specific submodules'', seems inappropriate because the section only covers Physics package (not ``submodules''). It should either be expanded with a short introduction listing other domain specific packages, or it should be renamed to ``Physics package''.
\begin{solution}
This section was renamed to "Physics submodule".  (See also the
discussion at~\ref{rev1point37} about module vs package).
\end{solution}

@@

To avoid confusion, and to be consistent with the definitions used by the
official Python documentation, we have modified the manuscript to use
``submodule'' to refer to any module that is a dotted submodule of
\texttt{sympy}, such as \texttt{sympy.physics.quantum}. This is to emphasize
that these modules all live within the \texttt{sympy} namespace, as ``module''
can suggest a separate library.
\end{solution}

\question The sentences in lines 657--661 should swap places, because ``areas of mathematics'' are discrete mathematics, concrete mathematics, etc., while simplifying expressions, performing common calculus operations, pretty printing expressions, etc.\ belongs to common operations (``other areas'' is also fine, albeit slightly wrong).
\begin{solution}
The ``areas of mathematics'' was intended to encompass all mathematical
operations. We have rewritten the first sentence as
\begin{quote}
SymPy supports a wide array of mathematical facilities.
\end{quote}
We have also changed ``other included areas'' to ``other supported facilities'' in the third sentence.

The order of the subsequent sentences was chosen to match the order they were
presented in the paper, so we have left them as-is.
\end{solution}

\question In line 662 ``classical mechanics and quantum mechanics'' are listed as the only example of the support for specific domains, as in section 5, which leaves the impression that physics the only one. Either more domains should be listed, or it should be reworded to recognize the fact that there are no others.
\begin{solution}
Physics is a very wide subject, so it would be too rough description to mention
it in the way you suggest, as a single domain.  Also, we list here only two of mentioned above
submodules in the \texttt{sympy.physics}, so \emph{there are} others.

We believe the current wording does make sense.
\end{solution}

### 2016-09-11 supplement.tex
Use Title Case consistently in section titles
Add an introduction for the supplement; address point 43 of the reviewer 3

\section{Limits: The Gruntz Algorithm}

\input{gruntz.tex}

% Series module (Formal Power Series, Fourier Series)
\section{Series}

\input{series.tex}

% Logic module
\section{Logic}

\input{logic}

\section{Diophantine Equations}

\input{diophantine}

% Sets
\section{Sets}
\input{sets}

\section{Category Theory}
\input{categories}

@@

\section{Comparison with Mathematica}

\input{comparison_with_mma}

\section{Other Projects that use SymPy}

\input{other_projects_that_use_sympy}

\section{Tensors}

\input{tensors}

\section{Numerical simplification}

\input{nsimplify}

\section{Examples}

\input{examples}

\section{References}

>>>>

Section \ref{suppsec:Gruntz} discusses the Gruntz algorithm, used to
calculate limits in the SymPy.  Sections \ref{suppsec:Series}--\ref{suppsec:Ten}
discuss in depth some selected submodules.  Section \ref{suppsec:numsimpl}
discusses numerical simplification.  Section \ref{suppsec:examples} provides
additional examples for topics, discussed in the main paper.  In sections
\ref{sympy-gamma} and \ref{sympy-live} introduced the SymPy Gamma
and the SymPy Live projects.  Finally, section \ref{comp-mma} do
brief comparison of the SymPy with the Wolfram Mathematica and the
section \ref{other-proj} lists some projects that depend on SymPy.

\section{Limits: The Gruntz Algorithm}
\label{suppsec:Gruntz}
\input{gruntz.tex}

% Series module (Formal Power Series, Fourier Series)
\section{Series}
\label{suppsec:Series}
\input{series.tex}

% Logic module
\section{Logic}
\label{suppsec:Logic}
\input{logic}

\section{Diophantine Equations}
\label{suppsec:Dioph}
\input{diophantine}

% Sets
\section{Sets}
\label{suppsec:Sets}
\input{sets}

\section{Statistics}
\label{suppsec:Stats}
\input{stats}

\section{Category Theory}
\label{suppsec:Cat}
\input{categories}

\section{Tensors}
\label{suppsec:Ten}
\input{tensors}

\section{Numerical Simplification}
\label{suppsec:numsimpl}
\input{nsimplify}

\section{Examples}
\label{suppsec:examples}
\input{examples}

@@

\section{Comparison with Mathematica}
\label{comp-mma}
\input{comparison_with_mma}

\section{Other Projects that Use SymPy}
\label{other-proj}
\input{other_projects_that_use_sympy}
